404 -- Page Not Found   

### 2025-09-10 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Updated DCC_2025 include with official publication link

---
title: "The Lipid Interactome"
subtitle: "An interactive and open access platform for exploring cellular lipid-protein interactomes"
date: 2025-02-04
keywords:
  - Lipid-protein interactions
  - Proteomics
  - Interactomics
  - Database
  - Multifunctionalized lipids

@@

Gaelen Guzman^1,^*, André Nadler^2^, Frank Stein^3^, Jeremy M. Baskin^4^, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Max Plank Institute of Molecular Cell Biology and Genetics, Dresden Germany; ^3^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^4^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

>>>>

---
title: "The Lipid Interactome:"
subtitle: "An interactive and open access platform for exploring cellular lipid-protein interactions"
date: 2025-02-04
keywords:
  - Lipid-protein interactions
  - Proteomics
  - Interactomics
  - Database
  - Multifunctionalized lipids

@@

Gaelen Guzman^1,^*, André Nadler^3^, Frank Stein^4^, Jeremy M. Baskin^5^, Carsten Schulz^2^, Fikadu G. Tafesse^1,2^

^1^Department of Molecular Immunology & Immunology, Oregon Health & Science University, Portland, OR, USA; ^2^Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^3^Max Plank Institute of Molecular Cell Biology and Genetics, Dresden Germany; ^4^Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^5^Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; *Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

### 2025-09-10 IndividualStudies/DCC_2025.qmd
Updated DCC_2025 include with official publication link

---
title: "Chiu et al. 2025"
subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
date: 2025-03-06
format: 
  html:
    embed-resources: false
standalone: false
---

>>>>

---
title: "Chiu et al. 2025"
subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
date: 2025-09-05
format: 
  html:
    embed-resources: false
standalone: false
---

### 2025-09-10 StudyInformation_includes/DCC_2025_include.qmd
Updated DCC_2025 include with official publication link

#### Journal
ChemR&Chi;iv

<https://doi.org/10.26434/chemrxiv-2025-j8nqz>{target="_blank"}

#### Abstract
Most eukaryotic membranes comprise phospholipids bearing two hydrophobic tails, but N-acylphosphatidylethanolamine (NAPE) stands out as a long-known but poorly understood phospholipid with three hydrophobic groups. What little attention that NAPE has received has been devoted to understanding its metabolic functions as a precursor to N-acylethanolamines, bioactive lipids that act as endocannabinoids. Yet, levels of NAPE increase during myocardial infarction and ischemia, suggesting potential signaling roles for this lipid. Here, we exploit photoaffinity labeling (PAL) to identify NAPE-interacting proteins and elucidate signaling functions of NAPE. By positioning diazirine and alkyne groups in metabolically distinct regions of the NAPE molecule, we ensured that our PAL probe reported on interactions of NAPE and not NAE. Our studies identified several NAPE interactors, including two single-pass transmembrane proteins, CD147/Basigin and CD44, both of which serve as chaperones for monocarboxylate transporters (MCTs) from the SLC16A family that mediate lactate flux across the plasma membrane. Functional studies revealed that NAPE stimulates lactate efflux by MCTs dependent upon CD147 and CD44, establishing NAPE as a bona fide signaling lipid and pointing to potential physiological roles in metabolic and energy homeostasis that may be pathologically relevant in ischemia.

>>>>

#### Journal
Journal of the American Chemical Society

<https://doi.org/10.1021/jacs.5c03851>{target="_blank"}

#### Abstract
Most eukaryotic membranes comprise phospholipids bearing two hydrophobic tails, but N-acylphosphatidylethanolamine (NAPE) stands out as a long-known but poorly understood phospholipid with three hydrophobic groups. What little attention NAPE has received has been devoted to understanding its metabolic functions as a precursor to N-acylethanolamine (NAE), a bioactive lipid that acts as an endocannabinoid. Yet, levels of NAPE increase during myocardial infarction and ischemia, suggesting potential signaling roles for this lipid. Here, we exploit photoaffinity labeling (PAL) to identify NAPE-interacting proteins and elucidate signaling functions of NAPE. By positioning diazirine and alkyne groups in metabolically distinct regions of the NAPE molecule, we ensured that our PAL probe reported on interactions of NAPE and not NAE. Our studies identified several NAPE interactors, including two single-pass transmembrane proteins, CD147/Basigin and CD44, both of which serve as chaperones for monocarboxylate transporters (MCTs) from the SLC16A family that mediate lactate flux across the plasma membrane. Functional studies revealed that NAPE stimulates lactate efflux by MCTs dependent upon CD147 and CD44, establishing NAPE as a bona fide signaling lipid and pointing to potential physiological roles in metabolic and energy homeostasis that may be pathologically relevant in ischemia.
